---
title: "Utility Check"
output:
html_document:
toc:
theme: united
---

<H1> Simulated Data - Simple Approach</H1>


# Method
A multivariate normal distribution was fitted separately for each outcome of variable sex
to the continuous variables with the exception of sat_sum. This variable
was later recalculated by the sum of the variables sat_v and sat_m. 


```{r, echo = FALSE, output = TRUE, fig.show= TRUE, warning= FALSE, message = FALSE}
setwd("C:/Users/Hariolf/Documents/GitHub/Synthetic_Data_Challenge")
load(paste0(getwd(), "/results/results_sat2.RData"))
library(corrplot)
par(mfrow = c(1,2))

# Graphical comparison for Margins
results_syn_sat_mnorm_simple$comp 

# Correlation plots for graphical comparison of Pearson Correlation
corrplot(results_syn_sat_mnorm_simple$cp1$corr, method = "color", type = "lower", main = "Original")
corrplot(results_syn_sat_mnorm_simple$cp2$corr, method = "color", type = "lower", main = "Synthetic")

# Very basic measures for testing analysis

# mean relative deviation of coefficients
results_syn_sat_mnorm_simple$cio$mrd_coef

# mean relative  deviation of coefficients
results_syn_sat_mnorm_simple$cio$mrd_se

# share of variables in the synthetic dataset that do not significantly differ from the distribution in the original dataset 
mean(results_syn_sat_mnorm_simple$ks > 0.05)

# Information loss measure proposed by Andrzej Mlodak (R-Package: sdcMicro)
results_syn_sat_mnorm_simple$il

# Distributional comparison of synthesised data (R-Package: synthpop) by (S_)pmSE
results_syn_sat_mnorm_simple$ug

# Two-way tables comparison of synthesised data (R-Package: synthpop) by (S_)pmSE
results_syn_sat_mnorm_simple$ut

```


<H1> Simulated Data - Complex Approach</H1>


# Method
A multivariate non-normal distribution considering skewness and curtosis was fitted separately for each outcome of variable sex to the continuous variables with the exception of sat_sum. This variable
was later recalculated by the sum of the variables sat_v and sat_m. 


```{r, echo = FALSE, output = TRUE, fig.show= TRUE, warning= FALSE, message = FALSE}
setwd("C:/Users/Hariolf/Documents/GitHub/Synthetic_Data_Challenge")

load(paste0(getwd(), "/results/results_sat2.RData"))

library(corrplot)
par(mfrow = c(1,2))

# Histograms for graphical comparison for Margins
results_syn_sat_mnorm_complex$comp

# Correlation plots for graphical comparison of Pearson Correlation
corrplot(results_syn_sat_mnorm_complex$cp1$corr, method = "color", type = "lower", main = "Original")
corrplot(results_syn_sat_mnorm_complex$cp2$corr, method = "color", type = "lower", main = "Synthetic")


# Very basic measures for testing analysis

# mean relative deviation of coefficients
results_syn_sat_mnorm_complex$cio$mrd_coef

# mean relative deviation of coefficients
results_syn_sat_mnorm_complex$cio$mrd_se

# share of variables in the synthetic dataset that do not significantly differ from the distribution in the original dataset 
mean(results_syn_sat_mnorm_complex$ks > 0.05)

# Information loss measure proposed by Andrzej Mlodak (R-Package: sdcMicro)
results_syn_sat_mnorm_complex$il

# Distributional comparison of synthesised data (R-Package: synthpop) by (S_)pmSE
results_syn_sat_mnorm_complex$ug

# Two-way tables comparison of synthesised data (R-Package: synthpop) by (S_)pmSE
results_syn_sat_mnorm_complex$ut

```




<H1> IPSO </H1>

```{r, echo = FALSE, output = TRUE, fig.show= TRUE, warning= FALSE, message = FALSE}
setwd("C:/Users/Hariolf/Documents/GitHub/Synthetic_Data_Challenge")

load(paste0(getwd(), "/results/results_sat2.RData"))
library(corrplot)
par(mfrow = c(1,2))

# Histograms for graphical comparison for Margins
results_sm_ipso_regsdc_conf_hs_fy$comp

# Correlation plots for graphical comparison of Pearson Correlation
corrplot(results_sm_ipso_regsdc_conf_hs_fy$cp1$corr, method = "color", type = "lower", main = "Original")
corrplot(results_sm_ipso_regsdc_conf_hs_fy$cp2$corr, method = "color", type = "lower", main = "Synthetic")

# Very basic measures for testing analysis

# mean relative deviation of coefficients
results_sm_ipso_regsdc_conf_hs_fy$cio$mrd_coef

# mean relative deviation of coefficients
results_sm_ipso_regsdc_conf_hs_fy$cio$mrd_se

# share of variables in the synthetic dataset that do not significantly differ from the distribution in the original dataset 
mean(results_sm_ipso_regsdc_conf_hs_fy$ks > 0.05)

# Information loss measure proposed by Andrzej Mlodak (R-Package: sdcMicro)
results_sm_ipso_regsdc_conf_hs_fy$il

# Distributional comparison of synthesised data (R-Package: synthpop) by (S_)pmSE
results_sm_ipso_regsdc_conf_hs_fy$ug

# Two-way tables comparison of synthesised data (R-Package: synthpop) by (S_)pmSE
results_sm_ipso_regsdc_conf_hs_fy$ut

```



<H1> FCS CART </H1>

```{r, echo = FALSE, output = TRUE, fig.show= TRUE, warning= FALSE, message = FALSE}
setwd("C:/Users/Hariolf/Documents/GitHub/Synthetic_Data_Challenge")

load(paste0(getwd(), "/results/results_sat2.RData"))
library(corrplot)
par(mfrow = c(1,2))

# Histograms for graphical comparison for Margins
results_sm_sat_fcs_cart$comp

# Correlation plots for graphical comparison of Pearson Correlation
corrplot(results_sm_sat_fcs_cart$cp1$corr, method = "color", type = "lower", main = "Original")
corrplot(results_sm_sat_fcs_cart$cp2$corr, method = "color", type = "lower", main = "Synthetic")

# Very basic measures for testing analysis

# mean relative deviation of coefficients
results_sm_sat_fcs_cart$cio$mrd_coef

# mean relative deviation of coefficients
results_sm_sat_fcs_cart$cio$mrd_se

# share of variables in the synthetic dataset that do not significantly differ from the distribution in the original dataset 
mean(results_sm_sat_fcs_cart$ks > 0.05)

# Information loss measure proposed by Andrzej Mlodak (R-Package: sdcMicro)
results_sm_sat_fcs_cart$il

# Distributional comparison of synthesised data (R-Package: synthpop) by (S_)pmSE
results_sm_sat_fcs_cart$ug

# Two-way tables comparison of synthesised data (R-Package: synthpop) by (S_)pmSE
results_sm_sat_fcs_cart$ut

```





<H1> GAN CTGAN </H1>

```{r, echo = FALSE, output = TRUE, fig.show= TRUE, warning= FALSE, message = FALSE}
setwd("C:/Users/Hariolf/Documents/GitHub/Synthetic_Data_Challenge")

load(paste0(getwd(), "/results/results_sat2.RData"))
library(corrplot)
par(mfrow = c(1,2))

# Histograms for graphical comparison for Margins
results_sm_sat_gan_ctgan$comp

# Correlation plots for graphical comparison of Pearson Correlation
corrplot(results_sm_sat_gan_ctgan$cp1$corr, method = "color", type = "lower", main = "Original")
corrplot(results_sm_sat_gan_ctgan$cp2$corr, method = "color", type = "lower", main = "Synthetic")

# Very basic measures for testing analysis

# mean relative deviation of coefficients
results_sm_sat_gan_ctgan$cio$mrd_coef

# mean relative deviation of coefficients
results_sm_sat_gan_ctgan$cio$mrd_se

# share of variables in the synthetic dataset that do not significantly differ from the distribution in the original dataset 
mean(results_sm_sat_gan_ctgan$ks > 0.05)

# Information loss measure proposed by Andrzej Mlodak (R-Package: sdcMicro)
results_sm_sat_gan_ctgan$il


# Distributional comparison of synthesised data (R-Package: synthpop) by (S_)pmSE
results_sm_sat_gan_ctgan$ug

# Two-way tables comparison of synthesised data (R-Package: synthpop) by (S_)pmSE
results_sm_sat_gan_ctgan$ut

```





<H1> GAN EPOCH1000 </H1>

```{r, echo = FALSE, output = FALSE, fig.show= TRUE, warning= FALSE, message = FALSE}
library(corrplot)
setwd("C:/Users/Hariolf/Documents/GitHub/Synthetic_Data_Challenge")

par(mfrow = c(1,2))
load(paste0(getwd(), "/results/results_sat2.RData"))

# Histograms for graphical comparison for Margins
results_sm_sat_gan_ctgan_epoch1000$comp

# Correlation plots for graphical comparison of Pearson Correlation
corrplot(results_sm_sat_gan_ctgan_epoch1000$cp1$corr, method = "color", type = "lower", main = "Original")
corrplot(results_sm_sat_gan_ctgan_epoch1000$cp2$corr, method = "color", type = "lower", main = "Synthetic")

# Very basic measures for testing analysis

# mean relative deviation of coefficients
results_sm_sat_gan_ctgan_epoch1000$cio$mrd_coef

# mean relative deviation of coefficients
results_sm_sat_gan_ctgan_epoch1000$cio$mrd_se

# share of variables in the synthetic dataset that do not significantly differ from the distribution in the original dataset 
mean(results_sm_sat_gan_ctgan_epoch1000$ks > 0.05)

# Information loss measure proposed by Andrzej Mlodak (R-Package: sdcMicro)
results_sm_sat_gan_ctgan_epoch1000$il

# Distributional comparison of synthesised data (R-Package: synthpop) by (S_)pmSE
results_sm_sat_gan_ctgan_epoch1000$ug

# Two-way tables comparison of synthesised data (R-Package: synthpop) by (S_)pmSE
results_sm_sat_gan_ctgan_epoch1000$ut

```









