---
title: ACS Dataset Evaluation Report - FCS
subtitle: Use Case School testing
author: Steffen Moritz, Hariolf Merkle, Felix Geyer, Michel Reiffert, Reinhard Tent (DESTATIS)
date: January 28, 2022
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
    toc: true
    toc_depth: 1
# pdf_document:
#    toc: true
#    toc_depth: 1
---




```{r setup, include=FALSE}
## Global options
knitr::opts_chunk$set(cache = TRUE)
library("kableExtra")
```

```{r dataset, include=FALSE}
# Load Source Dataset
load(here::here("results/rt_acs_fcs_samp100000.rda"))
load(here::here("Evaluation_ACS_FCS/results_acs_fcs2.RData"))
#load(here::here("acs.RData"))
result <- results_acs_FCS
```
# Executive Summary

FCS is not only very useful for the generation of synthetic "SAT"-data, it is also very suitable to generate synthetic data from the ACS dataset. Basically all marginal distributions are aligning. With one extreme exception, the S_pMSE shows only values below 10. The Pearson correlation coefficients for binary and (semi-)continuous variables are also practically identical to those of the original dataset. Also the absolute difference in densities and the Bhattacharyya distance support the overall impression. Only Mlodak's information loss criterion indicates this synthetic dataset as mediocre useful.




Based on the results of this document, we rate the suitability of this synthetic dataset for the use cases as follows:

**Releasing to public: YES ** 

**Testing analysis: YES **

**Education: YES **

**Testing technology: YES**



# Dataset Considerations


# Method Considerations

Since computing time increases sharply, when applied to larger datasets, applying FCS to the ACS dataset was rather challenging. Our first idea was to find out which of the features correlate, in order to decide which of these features should be fed to the algorithm simultaneously. Unfortunately we found a rather complex network of connections between many of the variables and hence had the problem, that it was not clear how the dataset could be split up in order to reduce it’s complexity without losing correlations between the data. So we decided to first use a subsample of the dataset, by randomly drawing 100 000 data points (approx. 10%) of the original dataset and to apply the FCS method on all features. Again we chose to use the default settings of the method, i.e. the order of synthesisation of the variables in ascending order, and using the Classification and Regression Tree (CART) machine learning model for each variable.Since the computation time for this subsample only took a little more than one hour, we were optimistic that we could apply the algorithm to the whole dataset as well, before the end of the challenge. Unfortunately this was not the case, so our findings have to rely on our data sample.


# Utility Evaluation

Different utility measures are applied in this section. These utility measures are the basis of utility evaluation for the generated synthetic dataset. The R packages synthpop, sdcMicro and corrplot were used to compute the following metrics. We do not use tests incorporating significance here. Confidence intervals in large surveys often tend to be extremely small so many slight differences appear to be significant. We do not consider the variable PUMA for our utility evaluation. During the ACS reports, some minor changes in availability regarding plots might occur. This is caused by the application of standardised scripts on different synthetic datasets.

### Graphical Comparison for Margins (R-Package: synthpop)

The following histograms provide an ad-hoc overview on the marginal distributions of the original and synthetic dataset. Matching or close distributions are related to a high data utility.

```{r, echo = FALSE, warning=FALSE, message=FALSE, fig.show= TRUE, results = 'hide'}
result$comp1$plots
result$comp2$plots
result$comp3$plots
result$comp4$plots
result$comp5$plots

```





### Correlation Plots for Graphical Comparison of Pearson Correlation 

Synthetic Datasets should represent the dependencies of the original datasets. The following correlation plots provide an ad-hoc overview on the Pearson correlations of the original and synthetic dataset. The left plot shows the original correlation whereas the right plot provides the correlation based on the synthetic dataset.


```{r, echo = FALSE, warning=FALSE, message=FALSE}
library("corrplot")
par(mfrow=c(1,2))
corrplot(results_acs_FCS[[5]], method = "color", type = "lower")
corrplot(results_acs_FCS[[6]], method = "color", type = "lower")
```





### Distributional Comparison of Synthesised Data (R-Package: synthpop) by (S_)pMSE

Propensity scores are calculated on a combined dataset (original and synthetic). A model (here: CART) tries to identify the synthetic units in the dataset. Since both datasets should be identically structured, the pMSE should equal zero. The S_pMSE (standardised pMSE) should not exceed 10 and for a good fit below 3 according to Raab (2021, https://unece.org/sites/default/files/2021-12/SDC2021_Day2_Raab_AD.pdf)

```{r, echo = FALSE, warning=FALSE, message=FALSE}
ug1 <- result$comp1$tab.utility
kbl(ug1) %>%
  kable_paper(full_width = F) 
```

```{r, echo = FALSE, warning=FALSE, message=FALSE}
ug1 <- data.frame(pMSE = result$ug1$pMSE, S_pMSE = result$ug1$S_pMSE)
kbl(ug1) %>%
  kable_paper(full_width = F) 
```

```{r, echo = FALSE, warning=FALSE, message=FALSE}
ug1 <- result$comp2$tab.utility
kbl(ug1) %>%
  kable_paper(full_width = F) 
```

```{r, echo = FALSE, warning=FALSE, message=FALSE}
ug1 <- data.frame(pMSE = result$ug2$pMSE, S_pMSE = result$ug2$S_pMSE)
kbl(ug1) %>%
  kable_paper(full_width = F) 
```

```{r, echo = FALSE, warning=FALSE, message=FALSE}
ug1 <- result$comp3$tab.utility
kbl(ug1) %>%
  kable_paper(full_width = F) 
```

```{r, echo = FALSE, warning=FALSE, message=FALSE}
ug1 <- data.frame(pMSE = result$ug3$pMSE, S_pMSE = result$ug3$S_pMSE)
kbl(ug1) %>%
  kable_paper(full_width = F) 
```

```{r, echo = FALSE, warning=FALSE, message=FALSE}
ug1 <- result$comp4$tab.utility
kbl(ug1) %>%
  kable_paper(full_width = F) 
```

```{r, echo = FALSE, warning=FALSE, message=FALSE}
ug1 <- data.frame(pMSE = result$ug4$pMSE, S_pMSE = result$ug4$S_pMSE)
kbl(ug1) %>%
  kable_paper(full_width = F) 
```

```{r, echo = FALSE, warning=FALSE, message=FALSE}
ug1 <- result$comp5$tab.utility
kbl(ug1) %>%
  kable_paper(full_width = F) 
```

```{r, echo = FALSE, warning=FALSE, message=FALSE}
ug1 <- data.frame(pMSE = result$ug5$pMSE, S_pMSE = result$ug5$S_pMSE)
kbl(ug1) %>%
  kable_paper(full_width = F) 
```



### Two-way Tables Comparison of Synthesised Data (R-Package: synthpop) by (S_)pMSE

Two-way tables are evaluated based on the original and the synthetic dataset based on S_pMSE (see above). We also present the results for the mean absolute difference in densities (MabsDD) and the Bhattacharyya distance (dBhatt).



```{r, echo = FALSE, warning=FALSE, message=FALSE}


#result$ut$utility.plot

result$ut1_1$utility.plot
result$ut1_2$utility.plot
result$ut1_3$utility.plot
result$ut1_4$utility.plot
result$ut1_5$utility.plot

```


```{r, echo = FALSE, warning=FALSE, message=FALSE}


#result$ut$utility.plot

result$ut2_1$utility.plot
result$ut2_2$utility.plot
result$ut2_3$utility.plot
result$ut2_4$utility.plot
result$ut2_5$utility.plot

```

```{r, echo = FALSE, warning=FALSE, message=FALSE}


#result$ut$utility.plot

result$ut3_1$utility.plot
result$ut3_2$utility.plot
result$ut3_3$utility.plot
result$ut3_4$utility.plot
result$ut3_5$utility.plot

```




### Information Loss Measure Proposed by Andrzej Mlodak (R-Package: sdcMicro)

The value of this information loss criterion is between 0 (no information loss) and 1. It is calculated overall and for each variable.

```{r, echo = FALSE, warning=FALSE, message=FALSE}

result$il

```


# Tuning and Optimizations
